Preliminary results for predicting adverse CDI outcomes

### 2022-04-05 workflow/notebooks/preliminary_2022-04-04.Rmd
Use knitr::kable() for markdown tables

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r deps}
library(tidyverse)
library(here)
library(data.table)

@@

```{r cdi-cases}
idsa_sra %>% group_by(cdiff_case) %>% tally()
```

@@

```{r cdi-cases_one-per-patient}
idsa_sra %>% filter_first_samples() %>% group_by(cdiff_case) %>% tally()
```

@@

```{r idsa}
cases_severity_OTUs_idsa %>% group_by(idsa) %>% tally()
```

@@

```{r attrib}
cases_severity_OTUs_attrib %>% group_by(attrib) %>% tally()
```

@@

```{r allcause}
one_sample_per_patient_allcause %>% filter(cdiff_case == 'Case') %>%  group_by(attrib, unattrib, allcause) %>% tally()
cases_severity_OTUs_allcause %>% group_by(allcause) %>% tally()
```

@@

```{r sum}
case_dat <- full_join(one_sample_per_patient_idsa, 
                      one_sample_per_patient_allcause, 
                      by = c('sample_id', 'patient_id', 'Run', 'collection_date', 'cdiff_case')
                      ) %>% 
  filter(cdiff_case == 'Case') %>% 
  rename(idsa = idsa_severity)
case_dat %>% 
  group_by(idsa, attrib, unattrib) %>% 
  tally()
case_dat %>% 
  group_by(idsa, allcause) %>% 
  tally()
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r deps}
library(data.table)
library(here)
library(knitr)
library(tidyverse)

@@

```{r cdi-cases}
idsa_sra %>% group_by(cdiff_case) %>% tally() %>% kable()
```

@@

```{r cdi-cases_one-per-patient}
idsa_sra %>% filter_first_samples() %>% group_by(cdiff_case) %>% tally() %>% kable()
```

@@

```{r idsa}
cases_severity_OTUs_idsa %>% group_by(idsa) %>% tally() %>% kable()
```

@@

```{r attrib}
cases_severity_OTUs_attrib %>% group_by(attrib) %>% tally() %>% kable()
```

@@

```{r allcause}
one_sample_per_patient_allcause %>% filter(cdiff_case == 'Case') %>%  group_by(attrib, unattrib, allcause) %>% tally() %>% kable()
cases_severity_OTUs_allcause %>% group_by(allcause) %>% tally() %>% kable()
```

@@

```{r sum}
case_dat <- full_join(one_sample_per_patient_idsa, 
                      one_sample_per_patient_allcause, 
                      by = c('sample_id', 'patient_id', 'Run', 'collection_date', 'cdiff_case')
                      ) %>% 
  filter(cdiff_case == 'Case') %>% 
  rename(idsa = idsa_severity)
case_dat %>% 
  group_by(idsa, attrib, unattrib) %>% 
  tally() %>% kable()
case_dat %>% 
  group_by(idsa, allcause) %>% 
  tally() %>% kable()
```
